Robot Team III: Scotty Strikes Back

### 2024-05-07 paper/paper.tex
updated introduction further...

% 3. Unsupervised ML
To complement these capabilities...

Therefore, unsupervised techniques to segment HSI and identify unique spectral signatures are needed for near-real time applications where detailed knowledge of contaminants may not be available

>>>>

% 3. Unsupervised ML

To take full advantage of the information contained in HSI for near-real time water quality analysis, unsupervised methods that segment HSI pixels and can extract relevant spectral endmembers are needed.

A variety of technqiues have

Data-driven techniques such as principal component analysis (PCA), independent component analysis (ICA), and k-nearest neighbors (kNN) have been widely employed for HSI analysis \cite{yousefi2016mineral,} (other citations). While useful, these methods

Geometric methods such as vertex component analysis (VCA) offer another approach based on the fact that endmember spectra form vertices of a simplex \cite{}. However, these approaches

Deep learning strategies such as autoencoders...

Principal component analysis (PCA) has been widely used for this task as it enables both dimensionality reduction and feature extraction.

Principal component analysis (PCA) is a popular choice for both dimenionsality reduction and feature extraction.

Principal component analysis (PCA) is a common method utilized for both dimensionality reduction and feature extraction

Dimensionality Reduction
Unsupervised Classification
Endmember Extraction and Spectral Unmixing

Goal: a principled unsupervised method that can both segment HSI imagery and aid in the extraction of relevant spectral endmembers
